---
geometry: "left=0.6in,right=0.6in,top=1.85cm,bottom=5cm"
fontsize: 12pt
classoption: landscape
header-includes: 
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage[table]{xcolor}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage[normalem]{ulem}
   \usepackage{graphicx}
   \usepackage{fancyhdr}
   \usepackage{caption}
   \captionsetup{width=\textwidth}
   \usepackage[labelformat=empty]{caption}
   \pagestyle{fancy}
   \setlength\headheight{70pt}
   \renewcommand{\headrulewidth}{0pt}
   \fancyhead[C]{\includegraphics[height = 1.5in]{/Users/mayracoronadogarcia/Documents/GitHub/HKCSPracticum/HKCS_LogoNew.jpg}}
   \fancyfoot[LE, LO]{Healthy Kids Colorado Survey}
   \fancyfoot[RE, RO]{www$.healthykidscolo$.org}

output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include = FALSE}
# Load Trend Function
source("/Users/mayracoronadogarcia/Documents/GitHub/HKCSPracticum/Trend_Analysis_Function.R")

# Run Trend Function
# district.data = hkcs.data.complete[which(hkcs.data.complete$District_Name == district), ]

hkcs.results = hkcs.trend.analysis(district_name = district,
                                   state = state.var,
                                   data = hkcs.data.complete, 
                                   fpc.data = fpc.data.var,
                                   fpc.var = fpc.var, 
                                   hkcs.strata = hkcs.strata.var,
                                   hkcs.survey.year = survey.year.var,
                                   hkcs.classid = classid.var,
                                   hkcs.schoolid = schoolid.var,
                                   moda.weight = moda.weight.var,
                                   modb.weight = modb.weight.var,
                                   core.weight = core.weight.var,
                                   trend = "Yes",
                                   prefix = prefix.var,
                                   variables = variables.var)

# save sample size numbers for each year
ss = hkcs.results[[1]]
ss.2013 = ss[which(ss$`Survey Year` == 2013), "Number of Respondents"]
ss.2015 = ss[which(ss$`Survey Year` == 2015), "Number of Respondents"]
ss.2017 = ss[which(ss$`Survey Year` == 2017), "Number of Respondents"]
```

### `r hkcs.results[[3]]`
### Examining Indicators from 2013 to 2017

This report presents your district's results from 2013, 2015, and 2017 Healthy Kids Colorado Survey (HKCS). The HKCS is a voluntary survey that is used to better understand youth health and well-being in Colorado. The HKCS is supported by the Colorado Department of Public Health and Environment, Colorado Department of Education, Colorado Department of Safety, and Colorado Department of Human Services. A team at the Colorado School of Public Health administers the survey. Website: www.healthykidscolo.org | Email: hkcs@ucdenver.edu

The HKCS collects self-reported health information from Colorado public high and middle school students every other year. The survey is conducted by sampling schools and classrooms to participate. Any school can opt-in and in some schools all students are invited to participate. When the student response rate is greater than 30%, the responses are weighted to the school and/or district enrollmemt. The number of students who completed the survey varied each year the survey was administered. For this district, `r ss.2013` students completed the survey in 2013, `r ss.2015` students completed the survey in 2015, and `r ss.2017` students completed the survey in 2017.

In the table below, each indicator is listed with the estimated percentage and 95% confidence interval of students answering yes in 2013, 2015, and 2017. Additionally, if requested, a trend analysis was conducted for each indicator from 2013 to 2017. If there is a statistically significant change the word **increase** or **decrease** is shown. A blank is shown if there was not a statistically significant change. These results can be used to inform if there is a change in student behaviors over time.


```{r echo=FALSE}
library("knitr")
library("kableExtra")

# converts the results from the function to a data frame
percentages = as.data.frame(hkcs.results[[2]])

# results data frame to be a presentable table
percentages %>%
  kable("latex",
        longtable = T,
        booktabs = T, escape = F,
        align = c("l",rep("r", ncol(percentages)-1)),
        caption = "\\textbf{Percentage and 95 percent confidence interval of indicator in 2013, 2015, and 2017.}") %>%
  kable_styling(latex_options = c( "striped",
                                  "HOLD_position",
                                  "repeat_header"), full_width = T) %>% 
  row_spec(0, bold = TRUE, align = "c") %>%
  column_spec(1, width = "25em") %>%
  add_header_above(c(" " = 1, "Percentage (%)" = 3), bold = TRUE)

```

* A "\*" was used to identify estimates based on half the sample size because the question was either on module A or module B.
* Data are suppressed to ensure confidentiality when the number number of students responding is fewer than 30 and/or the number of students responding Yes is fewer than 3, 0 or 100 percent, as indicated by all period ".(.)". All percentages are rounded to the nearest tenth.

For more information about how to use your data, resources available, and other data or technical asistance requests, please email HKCS@ucdenver.edu

Website: www.healthykidscolo.org